\part{自我介绍}
\section{One}
A seasoned Frontend Development Professional with a solid foundation in Computer Science and Technology from Zhengzhou University (2008-2012), backed by 13 years of progressive experience in the tech industry.

My career journey has three key phases:

My career began as a Software Development Engineer at Acumen Solutions (2012-2015), where I built a robust foundation in full-stack development, working with technologies like PHP, WordPress, Yii, and Drupal, while also honing my skills in frontend web development and optimization.

I then advanced to the role of Senior Frontend Developer at PwC Technology (Shanghai) Co., Ltd. (2015-2018). During this period, I specialized in frontend projects using Ionic, AngularJS, and ReactJS, took on technical leadership responsibilities, and contributed to the development of the company's internal UI framework, Appkit for React.

For the past seven years (2018-2025) at Citigroup, I have held the position of Frontend Leader | AVP, evolving from a hands-on technical expert to a team manager. I have been instrumental in leading frontend teams (managing 7-8 developers), architecting solutions for complex projects using React and Angular, driving the adoption of engineering best practices, and ensuring the successful delivery of critical financial systems. My tenure here encapsulates a blend of deep technical expertise, leadership, and strategic project management.


\section{Two}
Good morning/afternoon. My name is Yunpeng Ma. It's a pleasure to be here.

I am a seasoned frontend leader with over 13 years of experience, specializing in building and mentoring high-performing teams and delivering complex, scalable web applications.

My career journey has three key phases:

It began with a strong full-stack foundation at Acumen Solutions, where I worked extensively with PHP, WordPress, and Drupal.

I then deepened my frontend expertise at PwC, transitioning to a Senior role and working with AngularJS and ReactJS.

For the past seven years at Citi, I've grown into a leadership role as a Frontend Leader and AVP. This is where I've combined my deep technical skills with my passion for people leadership.

Here are what I consider my key strengths that align with a leadership role:

Technical Leadership: I have hands-on experience in architecting solutions with both React and Angular. I've driven the adoption of best practices, built shared component libraries, and optimized CI/CD pipelines to improve team efficiency and code quality.

Team Building \& Mentorship: I've directly managed a team of 7-8 frontend developers. I'm experienced in the full lifecycle of team growth—from interviewing and hiring, to mentoring, conducting performance reviews, and fostering a culture of knowledge sharing through regular tech talks.

Project Delivery: I have a proven track record of leading projects from requirement analysis and technical planning all the way to successful delivery, ensuring we meet both business deadlines and compliance standards.

I'm not just a manager who writes code; I'm a technical leader who enjoys solving complex problems, empowering my team, and staying at the forefront of technology, which is why I actively use AI tools like Copilot and Cursor to push the boundaries of productivity.

I am very excited about the opportunity to bring this blend of technical depth and leadership experience to your team. Thank you.